Standard Evaluation
===================

```{r}
library(dplyr)
library(tidyr)
library(wrapr)
library(rlang)
```

I would like to be able to pass column names to tidyverse (or even
non-tidyverse) subsetting/filtering functions in a way that is clean and
aesthetically pleasing. Ideally, I would like to get away with not quoting
things that are not the column name.

Data
----

```{r}
keep = LETTERS[5:15]

df = data.frame(alphabet = LETTERS,count = rep(10,26))
```

Stuff
-----

The goal is to get a non-non-standard way of doing this:

```{r}
df %>% filter(alphabet %in% keep)
```

This works, but is unsatisfying:

```{r}
df %>% filter(eval(parse(text = paste(col,'%in% keep'))))
```

You can just give `filter_()` a string, but the docs say it's deprecated.

```{r}
df %>% filter_(paste(col,'%in% keep'))
```

For practical purposes, that's probably the right answer, but I'd prefer an 
answer that didn't require me to either use a deprecated function, or to put 
things that are actually symbols (`%in%`, `keep`) in a string.

Tidyverse apparently provides functions for this purpose, including `enquo()`,
`quo()`, `let()`, and `sym()`, but I don't understand them. There's a discussion
[here](https://github.com/tidyverse/rlang/issues/116).


The first suggestion there is to use `!! sym(var)`, but that does not appear to
work for my purposes. 

```{r}
df %>% filter(!! sym(paste(col,'%in% keep')))
```

That error is reasonably straighforward, and might lead one to believe that this
will work:

```{r}
df %>% filter(!! sym(col) %in% keep)
```

But it doesn't. I have a hypothesis as to why, but I don't know how to fix it. 
I _think_ that it's treating the contents of `col`, "alphabet" as an object
`alphabet`, but failing to understand that it's a column in the data frame. 
FWIW, this is exactly why I object to NSE in the first place. But I could also 
be wrong about what the error means. It's worth noting that the examples on
the linked page don't require a comparison statement, and they _do_ work:

```{r}
df %>% select(!! sym(col))
```

So the problem is with the comparison statement itself, not the tidyverse 
functions. I'm guessing something about scope when `!! sym(col)` gets evaluated?

Anyway. Onward.

I also found [this vignette](dplyr.tidyverse.org/articles/programming.html).

```{r}
v = quo(col)
df %>% filter(UQ(v) %in% keep)
```

That doesn't work, but let's look at v

```{r}
v
```

So the problem here is clearly that it's quoting my variable name. Useless.

```{r}
v = sym(col)
df %>% filter(UQ(v) %in% keep)
```

Solved it! First you cast the contents of `col` to a symbol with `sym`, then you
unquote it using `UQ()` instead of `!!` because you don't want `filter()` doing
anything else with those bangs.

Presumably you don't need the intermediate variable.

```{r}
df %>% filter(UQ(sym(col)) %in% keep)
```

So that's how it's done, and I learned something new, but also that is bullshit.
Treating column names like the strings they are should be trivially easy, not
a thing that requires calls to two obscure functions that took me an hour and a
half to find and (sort of) understand.
